DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Added stargaze chart

```{r echo =FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)

@@

### Clean FearFail ###
# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from seeting up a business.

@@

### Clean NascentEntre ###
# Remove X's in NascentEntre year columns
names(NascentEntre) <- gsub("X", "", names(NascentEntre))

@@

#### Import WDI Annual GDP Growth Data ####
WDIsearch('gdp')
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))

@@

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R3)

@@

# Plot graph
car::scatterplotMatrix(CompleteDataset)

>>>>

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Set working directory
setwd('~/Assign2Education/')

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)
library(stargazer)

@@

### Clean FearFail ###
# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.

@@

### Clean NascentEntre ###
# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.

# Remove X's in NascentEntre year columns
names(NascentEntre) <- gsub("X", "", names(NascentEntre))

@@

#### Import WDI Annual GDP Growth Data ####
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))

@@

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
summary(R3)

@@

# Plot graph
car::scatterplotMatrix(CompleteDataset)
```

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'} 
# Create regression output table
labels <- c('(Intercept)', 'Percent Perceived', 'Percent Fear',
            'Annual GDP Growth', 'Percent Opportunities')

stargazer::stargazer(R1, R2, R3, covariate.lables = labels, title = 'Linear Regression Estimates', digits = 2, type = 'html')
